% add to Table of content
\addcontentsline{toc}{part}{ACKNOWLEDGMENTS}

% set 0 indentation
\setlength{\parindent}{0pt}
% set paragraph space = 1 space
\setlength{\parskip}{1em}
% set line space = 1
\setlength{\baselineskip}{1.2em} % this is the default value for line space = 1

\begin{center}
  \fontsize{14}{17}\selectfont{\textbf{
    ACKNOWLEDGMENTS
  }} \\
\end{center}
\vspace{36pt} 

I hold sincere gratitude towards my faculty advisor, Dr. Matthew N. Daily for his guidance, encouragement, and direction. I am extremely grateful to him for supporting my study, taking the time to review and correct my report, and for providing me with equipment even outside working hours. I would also like to extend my deepest gratitude to my examination committee members, Dr. Adisorn Lertsinsrubtavee and Dr.  Mongkol Ekpanyapong for their suggestions and time throughout the study. I would also like to express my deepest appreciation to Dr. Lertsinsrubtavee for his constant support and guidance. My thesis would not have been possible without Dr. Daily and Dr. Lertsinsrubtavee. 

I am deeply indebted to IntERLab for providing me with the infrastructure and networking equipment to complete my study.  I would like to express my heartfelt appreciation to Nunthaphat Weshsuwannarugs, Kalana Jayaratne, and Nisarat Tansakul for their help towards making the study realize into a real drone with a mesh network towards the end of my study. 

I would like to thank our CSIM secretary, Sireekant Thanwongpan, for scheduling and arranging presentation dates with my examination committee.

I also thank my parents, family, and friends who encouraged and supported me throughout the time of my study. I and extremely grateful to my mother for her continuous support and motivation to complete my study.